---
title: "Iteration"
output: html_notebook
editor_options:
  chunk_output_type: inline
---

```{r setup}
library(tidyverse)

# Generate student exam data
set.seed(1000)
exams <- list(
  student1 = round(runif(10, 50, 100)),
  student2 = round(runif(10, 50, 100)),
  student3 = round(runif(10, 50, 100)),
  student4 = round(runif(10, 50, 100)),
  student5 = round(runif(10, 50, 100))
)
```

## Your Turn 1

Here is a list:

```{r}
a_list <- list(num = c(8, 9),
               log = TRUE,
               alpha = as.list(letters[1:3]))
```

Here are two subsetting commands. Do they return the same values? Run the code chunk above, _and then_ run the code chunks below to confirm

```{r}
a_list["num"]
```

```{r}
a_list$num
```

## Your Turn 2

What will each of these return? Run the code chunks to confirm.

```{r}
vec <- c(-2, -1, 0, 1, 2)
abs(vec)
```

```{r}
lst <- list(-2, -1, 0, 1, 2)
abs(lst)
```

## List Iteration

Run the code in the chunks. What does it return?

```{r}
list(student1 = mean(exams$student1),
     student2 = mean(exams$student2),
     student3 = mean(exams$student3),
     student4 = mean(exams$student4),
     student5 = mean(exams$student5))
```

```{r}
map(exams, mean)
```

## Your Turn 3

Calculate the variance (`var()`) of each student’s exam grades.

```{r}

```

## Your Turn 4

Calculate the max grade (max()) for each student. Return the result as a vector.

```{r}

```

## Functions

Write out code that calculates a mean after dropping the lowest value.

```{r}
vec <- exams$student1
(sum(vec) - min(vec)) / (length(vec) - 1)
```

1. Write code that solves a problem
2. Convert code into a function by wrapping it with `function(){}`
3. Add an argument to pass in different values
4. Use `map_dbl()` to apply to all students


## Your Turn 5

Write a function that counts the best exam twice and then takes the average. Use it to grade all of the students.

```{r}

```


# Take Aways

Lists are a useful way to organize data, but you need to arrange manually for functions to iterate over the elements of a list.

You can do this with the `map()` family of functions in the purrr package.

To write a function,

1. Write code that solves the problem for a real object
2. Wrap the code in `function(){}` to save it
3. Add the name of the real object as the function argument

This sequence will help prevent bugs in your code (and reduce the time you spend correcting bugs).

