---
title: "tidymodels - Starter-Pack"
output: 
  rmdformats::robobook:
    toc_depth: 3
---


```{r, echo = FALSE}
# Reference: https://rviews.rstudio.com/2019/06/19/a-gentle-intro-to-tidymodels/

```




## Load Libraries

```{r, message = FALSE, }
library(tidymodels)
library(GGally)
library(corrr)

```
  - loads `dplyr` and `ggplot2`  


<br>
  

## Data
```{r}
iris %>% 
  as_tibble()

```



```{r, message = FALSE}
#pairwise plots
ggpairs(iris)


#pairwise corr
iris_cor <- iris %>% 
  as_tibble() %>% 
  select(where(is.numeric)) %>% 
  correlate() 

iris_cor %>% 
  rearrange() %>% 
  fashion() %>% 
  knitr::kable()

```



  
## Pre-Process

### Data Sampling
```{r}
set.seed(1234)

iris_split <- initial_split(iris, prop = 0.6)
iris_split


iris_split %>%
  training() %>%
  glimpse()

```




### Pre-Process Interface
```{r}
iris_recipe <- training(iris_split) %>%
  recipe(Species ~ .) %>%
  step_corr(all_predictors()) %>%
  step_center(all_predictors(), -all_outcomes()) %>%
  step_scale(all_predictors(), -all_outcomes()) %>%
  prep()

iris_training <- juice(iris_recipe)
glimpse(iris_training)

```

```{r}
# View recipe and operations
iris_recipe

```



### Execute the Pre-Processing
```{r}
iris_testing <- iris_recipe %>%
  bake(testing(iris_split)) 

glimpse(iris_testing)

```



## Model Training
```{r}

# ranger
iris_ranger <- rand_forest(trees = 100, mode = "classification") %>%
  set_engine("ranger") %>%
  fit(Species ~ ., data = iris_training)

```

```{r}
# randomForest
iris_rf <-  rand_forest(trees = 100, mode = "classification") %>%
  set_engine("randomForest") %>%
  fit(Species ~ ., data = iris_training)

```





## Predictions
```{r}
predict(iris_ranger, iris_testing)


iris_ranger %>%
  predict(iris_testing) %>%
  bind_cols(iris_testing)

```



## Model Validation
```{r}
iris_ranger %>%
  predict(iris_testing) %>%
  bind_cols(iris_testing) %>%
  metrics(truth = Species, estimate = .pred_class)


iris_rf %>%
  predict(iris_testing) %>%
  bind_cols(iris_testing) %>%
  metrics(truth = Species, estimate = .pred_class)

```


### Per Classifier Metrics
```{r}
iris_ranger %>%
  predict(iris_testing, type = "prob")


iris_probs <- iris_ranger %>%
  predict(iris_testing, type = "prob") %>%
  bind_cols(iris_testing)


iris_probs%>%
  roc_curve(Species, .pred_setosa:.pred_virginica) %>%
  autoplot()


```




```{r}
predict(iris_ranger, iris_testing, type = "prob") %>%
  bind_cols(predict(iris_ranger, iris_testing)) %>%
  bind_cols(select(iris_testing, Species)) %>%
  metrics(truth = Species, .pred_setosa:.pred_virginica, estimate = .pred_class)


predict(iris_rf, iris_testing, type = "prob") %>%
  bind_cols(predict(iris_rf, iris_testing)) %>%
  bind_cols(select(iris_testing, Species)) %>%
  metrics(truth = Species, .pred_setosa:.pred_virginica, estimate = .pred_class)

```


## Your Turn

How does model performance change when omitting some/all of the `step_x` recipe specifications?  

<br>

How does model performance change with different training/testing data splits?  






