---
title: "Hotel Bookings"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: img_hotel/grand-budapest.png
    theme: lumen
    source_code: embed
runtime: shiny

---


```{r global, include = FALSE}

# Libraries
library(tidymodels)  
library(shiny)

# Helper packages
library(readr)          # for importing data
library(DT)
library(wesanderson)
# library(janitor)     # for tabyl
# library(forcats)     # for factor operations


# Import data
hotels <- 
  # read_csv('https://tidymodels.org/start/case-study/hotels.csv') %>%
  read_csv(here::here('data/hotels.csv')) %>%
  mutate_if(is.character, as.factor) 

```




Sidebar {.sidebar}
===========================================================

<br>

`r h3("Objective:")`
`r h3("Predict which hotel stays include children.")`

<br>

- - -

<br>


```{r data.splitting}
# Data splitting and resampling
set.seed(123)
splits <- initial_split(hotels, strata = children)

hotel_other <- training(splits)
hotel_test  <- testing(splits)



# Create a validation set
set.seed(234)
prop.validation <- .20

val_set <- validation_split(hotel_other, 
                            strata = children, 
                            prop   = 1-prop.validation)

```




```{r create.model}
lr_mod <- 
  logistic_reg(mixture = 1, penalty = tune()) %>% 
  set_engine("glmnet")

```


```{r create.recipe}
holidays <- c("AllSouls", "AshWednesday", "ChristmasEve", "Easter", 
              "ChristmasDay", "GoodFriday", "NewYearsDay", "PalmSunday")

lr_recipe <- 
  recipe(children ~ ., data = hotel_other) %>%   #remember that `hotel_other` is just a template here
  step_date(arrival_date) %>% 
  step_holiday(arrival_date, holidays = holidays) %>% 
  step_rm(arrival_date) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_predictors())


```


```{r create.workflow}
lr_workflow <- 
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(lr_recipe)

```




Validation Summary
===========================================================


## Column {data-width="500"}

### Data Splitting

**Total Observations:**  
`r dim(hotels)[1] %>% scales::comma()`

**Training Set:**  
`r dim(hotel_other)[1] %>% scales::comma()`

**Validation Set:**  
`r (dim(hotel_other)[1] * prop.validation) %>% scales::comma()`

**Testing Set:**  
`r dim(hotel_test)[1] %>% scales::comma()`




### Data Viewer

```{r}
hotels %>% 
  slice(1:100) %>% 
  datatable(options = list(searching = FALSE,
                           pageLength = 50,
                           lengthMenu = c(50, 100),
                           scrollY = '300px',
                           scrollX = '300px'),
            style = "default")

```




## Column {data-width="500"}

### Case Imbalance Check

```{r}

lr_recipe %>%
  prep() %>%
  juice() %>% 
  ggplot(aes(children)) +
    geom_bar(fill = wes_palette("Moonrise3")[1])


```




### Penalty Validation

```{r}

```



Classification Results
===========================================================

## Column {data-width="500"}

### ROC

```{r}

```


### Confusion Matrix

```{r}

```


## Column {data-width="500"}

### Variable Importance Plot

```{r}

```

### Prediction Metrics

```{r}

```

