---
title: "Hotel Bookings"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: img_hotel/grand-budapest.png
    favicon: img_hotel/Mendls.png
    theme: lumen
    source_code: embed
runtime: shiny

---


```{r global, include = FALSE}

# Libraries
library(tidymodels)  
library(shiny)

# Helper packages
library(readr)          # for importing data
library(DT)
library(vip)            # for variable importance plots
library(wesanderson)
# library(janitor)     # for tabyl
# library(forcats)     # for factor operations


# Import data
hotels <- 
  # read_csv('https://tidymodels.org/start/case-study/hotels.csv') %>%
  read_csv(here::here('data/hotels.csv')) %>%
  mutate_if(is.character, as.factor) 

```




Sidebar {.sidebar}
===========================================================

<br>

`r h3("Objective:")`
`r h3("Predict which hotel stays include children.")`

<br>

- - -

<br>

```{r shiny.inputs}
dateRangeInput(
  inputId = "date_range", 
  label   = h4("Date Range"),
  start   = min(hotels$arrival_date), 
  end     = max(hotels$arrival_date), 
  min     = min(hotels$arrival_date), 
  max     = max(hotels$arrival_date), 
  startview = "month")

 renderPrint(input$date_range)

```



```{r data.filtered}
hotels_filtered <- reactive({
  hotels %>%
  filter(arrival_date %>% between(left  = input$date_range[1], 
                                  right = input$date_range[2]))
})

renderPrint(dim(hotels_filtered()))

```



```{r data.splitting}
# Data splitting and resampling
set.seed(123)

splits <- reactive({
  initial_split(hotels_filtered(), strata = children)
})


hotel_other <- reactive({
  training(splits())
})


hotel_test  <- reactive({
  testing(splits())
})


# Create a validation set
set.seed(234)
prop.validation <- .20

val_set <- reactive({
  validation_split(hotel_other(), 
                   strata = children, 
                   prop   = 1-prop.validation)
})

# renderPrint(val_set())


```




```{r create.model}
lr_mod <- 
  logistic_reg(mixture = 1, penalty = tune()) %>% 
  set_engine("glmnet")

```


```{r create.recipe}
holidays <- c("AllSouls", "AshWednesday", "ChristmasEve", "Easter", 
              "ChristmasDay", "GoodFriday", "NewYearsDay", "PalmSunday")

lr_recipe <- reactive({
  recipe(children ~ ., data = hotel_other()) %>%   #remember that `hotel_other` is just a template here
  step_date(arrival_date) %>% 
  step_holiday(arrival_date, holidays = holidays) %>% 
  step_rm(arrival_date) %>% 
  step_dummy(all_nominal(), -all_outcomes()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_predictors())
})

```


```{r create.workflow, eval = FALSE}
lr_workflow <- reactive({
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(lr_recipe())
})

```




Validation Summary
===========================================================


## Column {data-width="500"}

### Data Splitting

**Total Observations:**  
`r reactive(dim(hotels_filtered())[1] %>% scales::comma())`

**Training Set:**  
`r reactive(dim(hotel_other())[1] %>% scales::comma())`

**Validation Set:**  
`r reactive((dim(hotel_other())[1] * prop.validation) %>% scales::comma())`

**Testing Set:**  
`r reactive(dim(hotel_test())[1] %>% scales::comma())`




### Data Viewer

```{r}
output$data_viewer <- DT::renderDataTable({
hotels_filtered() %>% 
  # slice(1:100) %>% 
  datatable(options = list(searching = FALSE,
                           pageLength = 50,
                           lengthMenu = c(50, 100),
                           scrollY = '250px',
                           scrollX = '300px'),
            style = "default")
})

DT::dataTableOutput(outputId = "data_viewer")

```




## Column {data-width="500"}

### Case Imbalance Check

```{r, eval = TRUE}
output$case_plot <- renderPlot({
  lr_recipe() %>%
  prep() %>%
  juice() %>% 
  ggplot(aes(children)) +
    geom_bar(fill = wes_palette("GrandBudapest2")[4])
})

plotOutput(outputId = "case_plot")

```










### Penalty Validation

```{r}

```



Classification Results
===========================================================

## Column {data-width="500"}

### ROC

```{r}

```


### Confusion Matrix

```{r}

```


## Column {data-width="500"}

### Variable Importance Plot

```{r}

```

### Prediction Metrics

```{r}

```

