---
title: "Hotel Bookings"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: img_hotel/grand-budapest.png
    favicon: img_hotel/Mendls.png
    theme: lumen
    source_code: embed
runtime: shiny

---


```{r global, include = FALSE}

# Libraries
library(tidymodels)  
library(shiny)
library(shinyWidgets)
library(shinyjs)

# Helper packages
library(readr)          # for importing data
library(DT)
library(vip)            # for variable importance plots
library(wesanderson)
# library(janitor)     # for tabyl
# library(forcats)     # for factor operations


# Import data
hotels <- 
  # read_csv('https://tidymodels.org/start/case-study/hotels.csv') %>%
  read_csv(here::here('data/hotels.csv')) %>%
  mutate_if(is.character, as.factor) %>% 
  slice(1:5000)        #TEMPORARY FOR TESTING ------------


# For figure color scheme
hotel.palette <- wes_palette("GrandBudapest2")

```




Sidebar {.sidebar}
===========================================================

<br>

`r h3("Objective:")`
`r h3("Predict which hotel stays include children.")`

<br>

- - -

<br>

```{r shiny.inputs}

useShinyjs(rmd = TRUE)

dateRangeInput(
  inputId   = "date_range", 
  label     = h4("Date Range"),
  start     = min(hotels$arrival_date), 
  end       = max(hotels$arrival_date), 
  min       = min(hotels$arrival_date), 
  max       = max(hotels$arrival_date), 
  startview = "month")

# renderPrint(input$date_range)

br()

sliderInput(
  inputId = "training_slider",
  label   = h4("Training Data Proportion"),
  min     = 0.10,
  max     = 0.90,
  value   = 0.75,
  step    = 0.05,
  ticks   = FALSE)
  

br()
br()

shinyWidgets::switchInput(
   inputId    = "downsample",
   label      = "Down-Sample",
   value      = FALSE,
   labelWidth = "80px"
)


br()
hr()
br()


actionButton(inputId = "apply", label = "Apply", icon = icon("play"))
# renderPrint(input$apply)

actionButton(inputId = "reset", label = "Reset", icon = icon("sync"))
# renderPrint(input$reset)


# Reset action
observeEvent(eventExpr = input$reset, handlerExpr = {

  updateDateRangeInput(
    session = session, 
    inputId = "date_range", 
    start   = min(hotels$arrival_date), 
    end     = max(hotels$arrival_date)
  )
  
  
  updateSliderInput(
    session = session,
    inputId = "training_slider",
    value   = 0.75
  )
  
  
  updateSwitchInput(
    session  = session,
    inputId  = "downsample",
    value    = FALSE)
 
  
  # Have shinyjs click apply after a reset click
  shinyjs::delay(ms = 300, expr = {
    shinyjs::click(id = "apply")
  })
 
})  
  
```



```{r data.filtered}
hotels_filtered <- eventReactive(eventExpr = input$apply, 
                                             
  valueExpr = {
  
  hotels %>%
  filter(arrival_date %>% between(left  = input$date_range[1], 
                                  right = input$date_range[2]))
  },
  ignoreNULL = FALSE
)

# renderPrint(dim(hotels_filtered()))

```



```{r data.splitting}
# Data splitting and resampling
set.seed(123)


splits <- eventReactive(eventExpr = input$apply,

  valueExpr = {

  initial_split(hotels_filtered(),
                strata = children,
                prop   = input$training_slider)
  }, 
  ignoreNULL = FALSE
)


hotel_other <- reactive({
  training(splits())
})


hotel_test  <- reactive({
  testing(splits())
})


# Create a validation set
set.seed(234)
prop.validation <- .20

val_set <- reactive({
  validation_split(hotel_other(), 
                   strata = children, 
                   prop   = 1-prop.validation)
})

# renderPrint(val_set())


```




```{r create.model}
lr_mod <- 
  logistic_reg(mixture = 1, penalty = tune()) %>% 
  set_engine("glmnet")

```


```{r create.recipe}
holidays <- c("AllSouls", "AshWednesday", "ChristmasEve", "Easter", 
              "ChristmasDay", "GoodFriday", "NewYearsDay", "PalmSunday")


lr_recipe <- eventReactive(
  eventExpr = input$apply, 
  
  valueExpr = {
  
    if (!input$downsample) {
    
      recipe(children ~ ., data = hotel_other()) %>%   #remember that `hotel_other` is just a template here
      step_date(arrival_date) %>% 
      step_holiday(arrival_date, holidays = holidays) %>% 
      step_rm(arrival_date) %>% 
      step_dummy(all_nominal(), -all_outcomes()) %>% 
      step_zv(all_predictors()) %>% 
      step_normalize(all_predictors())
  
    } else {
  
      recipe(children ~ ., data = hotel_other()) %>%
      step_date(arrival_date) %>%
      step_holiday(arrival_date, holidays = holidays) %>%
      step_rm(arrival_date) %>%
      step_dummy(all_nominal(), -all_outcomes()) %>%
      step_zv(all_predictors()) %>%
      step_normalize(all_predictors()) %>%
      themis::step_downsample(children, under_ratio = 1)
    }
  }, 
  ignoreNULL = FALSE
)

```


```{r create.workflow}
lr_workflow <- reactive({
  workflow() %>% 
  add_model(lr_mod) %>% 
  add_recipe(lr_recipe())
})

```


```{r tuning.grid}
# `length.out` will deterrmine how many penalty values are tested in `tune_grid()`
lr_reg_grid <- tibble(penalty = 10^seq(-4, -1, length.out = 10))  ##30


# Train and tune the model
lr_tune <- reactive({
  lr_workflow() %>% 
  tune_grid(resamples = val_set(), #rset object
            grid      = lr_reg_grid,
            control   = control_grid(save_pred = TRUE), #needed to get data for ROC curve
            metrics   = metric_set(roc_auc))
})


lr_best <- reactive({
  lr_tune() %>% 
  select_best("roc_auc")
})

```


```{r best.workflow}
# Add best validation model to workflow
lr_workflow_best <- reactive({
  finalize_workflow(
  lr_workflow(),
  lr_best())       #needs to have the same column name as tune()
})

```


```{r fit.training}
# Inspect fit on entire training data
lr_fit <- reactive({
  lr_workflow_best() %>% 
  fit(hotel_other())
})

```


```{r last.fit}
lr_last_fit <- reactive({
  last_fit(
    lr_workflow_best(),
    splits())
})

```


```{r confusion.matrix}
lr_conf_mat <- reactive({
  lr_last_fit() %>%
  collect_predictions() %>% 
  conf_mat(truth = children, estimate = .pred_class) 
})


```






Validation Summary
===========================================================


## Column {data-width="500"}

### Data Splitting

**Total Observations:**  
`r reactive(dim(hotels_filtered())[1] %>% scales::comma())`

**Training Set:**  
`r reactive(dim(hotel_other())[1] %>% scales::comma())`

**Validation Set:**  
`r reactive((dim(hotel_other())[1] * prop.validation) %>% scales::comma())`

**Testing Set:**  
`r reactive(dim(hotel_test())[1] %>% scales::comma())`




### Data Viewer

```{r}
hotels %>% 
  slice(1:100) %>% 
  datatable(options = list(searching = FALSE,
                           pageLength = 50,
                           lengthMenu = c(50, 100),
                           scrollY = '250px',
                           scrollX = '300px'),
            style = "default")

```




## Column {data-width="500"}

### Case Imbalance Check

```{r}
output$case_plot <- renderPlot({
  lr_recipe() %>%
  prep() %>%
  juice() %>% 
  ggplot(aes(children)) +
    geom_bar(fill = hotel.palette[2])
})

plotOutput(outputId = "case_plot")

```










### Workflow

```{r}
# Report workflow with optimized `penalty`
renderPrint(lr_workflow_best())

```



Classification Results
===========================================================

## Column {data-width="500"}

### ROC

```{r}
# output$lr_auc <- renderPlot({
#   lr_tune() %>%
#   collect_predictions(parameters = lr_best()) %>%
#   roc_curve(children, .pred_children) %>%
#   autoplot()
# })


output$lr_auc <- renderPlot({
  lr_tune() %>%
  collect_predictions(parameters = lr_best()) %>%
  roc_curve(children, .pred_children) %>%
  ggplot(aes(x = 1 - specificity, y = sensitivity)) +
  geom_path(lwd = 1.2, color = hotel.palette[4]) +
  geom_abline(lty = 3, lwd = 1.2, color = hotel.palette[4]) +
  coord_equal() +
  theme_classic()
})

plotOutput(outputId = "lr_auc")


```


### Confusion Matrix

```{r}
# renderPrint(lr_conf_mat() %>% tidy())

output$conf_mat_plot <- renderPlot({
  lr_conf_mat() %>%
    autoplot(type = "heatmap")

})

plotOutput(outputId = "conf_mat_plot")

```


## Column {data-width="500"}

### Variable Importance Plot

```{r, vip.plot}
output$vip_plot <- renderPlot({
  lr_fit() %>%
    pull_workflow_fit() %>%
    vip(num_features = 20,
        aesthetics = list(color = hotel.palette[1], fill = hotel.palette[1], size = 0.3))
})

plotOutput(outputId = "vip_plot")

```

### Prediction Metrics

```{r}
output$metrics <- renderTable({
  lr_conf_mat() %>%
    summary() %>%
    select(-.estimator) 
})

tableOutput(outputId = "metrics")

```

